PLAE web app enables powerful searching and multiple visualizations across one million unified single-cell ocular transcriptomes

### 2022-08-30 manuscript_00.Rmd
halfway to updated heatmap

# tic()
# g <- consist_diff %>% filter(Symbol %in% uniq_g$Symbol) %>% group_by(Base) %>% slice_max(n=8, order_by = `mean log2FC`) %>% mutate(g = paste0(Symbol, ' (', ID, ')')) %>% pull(g)
# 
# consist_diff_long <- scEiaD_2020_v01 %>%
#   tbl("diff_testing") %>%
#   filter(Gene %in% g) %>%
#   collect() %>%
#   filter(Base %in% ws_oct,
#          Group == 'CellType (Predict)',
#          Against == 'All') %>%
#   select(Gene, Organism, log2FoldChange, Base)
# 
# consist_diff_wide <- consist_diff_long %>% 
#   mutate(GO = paste0(Base, '_', Organism)) %>% 
#   select(-Organism, -Base) %>% 
#   pivot_wider(values_from=log2FoldChange, names_from = GO)
# consist_diff_celltype <- colnames(consist_diff_wide[,-1])
# consist_diff_wide <- consist_diff_wide %>% data.frame()
# row.names(consist_diff_wide) <- consist_diff_wide$Gene
# 
# consist_diff_wide <- consist_diff_wide[,-1]
# 
# 
# 
# consist_diff_organism <- str_extract(consist_diff_celltype, '_\\w+ \\w+') %>% gsub('_','',.)
# consist_diff_cts  <- str_extract(consist_diff_celltype, '.*_') %>% gsub('_','',.)
# consist_diff_genes <- row.names(consist_diff_wide) %>% gsub(' \\(.*','',.)
# 
# consist_diff_base <- consist_diff_genes %>% as_tibble() %>% rename(Symbol = value) %>% left_join(consist_diff %>% select(Symbol, Base) %>% unique()) %>% pull(Base)

consist_diff_hm <- ComplexHeatmap::Heatmap(consist_diff_wide, column_labels = consist_diff_organism, 
                                           column_split = consist_diff_cts, 
                                           row_split = consist_diff_base, show_row_dend = FALSE, 
                                           row_labels = consist_diff_genes, 
                                           column_title_rot = 90, 
                                           name = 'log2FC', use_raster = TRUE,
                                           row_title_rot = 0)
ComplexHeatmap::draw(consist_diff_hm, padding = unit(c(0, 0, 1.5, 0), "in"), row_title = "Marker Genes")
#toc()
```

>>>>

# tic()
# g <- consist_diff %>% filter(Symbol %in% uniq_g$Symbol) %>% group_by(Base) %>% slice_max(n=8, order_by = `mean log2FC`) %>% mutate(g = paste0(Symbol, ' (', ID, ')')) %>% pull(g)
# 
# consist_diff_long <- scEiaD_2020_v01 %>%
#   tbl("diff_testing") %>%
#   filter(Gene %in% g) %>%
#   collect() %>%
#   filter(Base %in% ws_oct,
#          Group == 'CellType (Predict)',
#          Against == 'All') %>%
#   select(Gene, Organism, log2FoldChange, Base)
# 
# consist_diff_wide <- consist_diff_long %>% 
#   mutate(GO = paste0(Base, '_', Organism)) %>% 
#   select(-Organism, -Base) %>% 
#   pivot_wider(values_from=log2FoldChange, names_from = GO)
# consist_diff_celltype <- colnames(consist_diff_wide[,-1])
# consist_diff_wide <- consist_diff_wide %>% data.frame()
# row.names(consist_diff_wide) <- consist_diff_wide$Gene
# 
# consist_diff_wide <- consist_diff_wide[,-1]
# 
# 
# 
# consist_diff_organism <- str_extract(consist_diff_celltype, '_\\w+ \\w+') %>% gsub('_','',.)
# consist_diff_cts  <- str_extract(consist_diff_celltype, '.*_') %>% gsub('_','',.)
# consist_diff_genes <- row.names(consist_diff_wide) %>% gsub(' \\(.*','',.)
# 
# consist_diff_base <- consist_diff_genes %>% as_tibble() %>% rename(Symbol = value) %>% left_join(consist_diff %>% select(Symbol, Base) %>% unique()) %>% pull(Base)
cbind(consist_diff_genes, consist_diff_base) %>% as_tibble() %>% left_join(queries, by = c('consist_diff_genes' = 'Symbol', 'consist_diff_base' = 'Base'))

rand_nums <- floor(runif(nrow(consist_diff_wide), min=0, max=3))
rand_col <-  circlize::colorRamp2(c(-0, 1, 2), c("white", "gray", "black"))

consist_diff_hm <- ComplexHeatmap::Heatmap(consist_diff_wide, 
                                           column_labels = consist_diff_organism, 
                                           column_split = consist_diff_cts, 
                                           row_split = consist_diff_base, 
                                           show_row_dend = FALSE, 
                                           column_title_rot = 90, 
                                           name = 'log2FC', use_raster = TRUE,
                                           row_title_rot = 0) + 
  ComplexHeatmap::Heatmap(rand_nums,
                          row_split = consist_diff_base,
                          col = rand_col,
                          row_labels = consist_diff_genes,
                          column_labels = "Pubmed Gene Citations",
                          column_names_side = 'top')
ComplexHeatmap::draw(consist_diff_hm, padding = unit(c(0, 0, 1.5, 0), "in"), row_title = "Marker Genes")
#toc()
```
